---
output: github_document
---


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# histogramr

<!-- badges: start -->
<!-- badges: end -->

The goal of `histogramr` package is to help create histograms easily, using minimal inputs. The `histogram` function can also be tweaked and desired additions can be made to it. Additionally, it can handle errors and give error messages (if any) based on the input.

## Installation

You can install the development version of histogramr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat545ubc-2023/histogramr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(histogramr)

# Example used from the `cancer_sample` dataset from the `datateachr` package.

#Laod `datateachr` package
library(datateachr)

hist1 <- histogram(cancer_sample, var = "area_worst")
print(hist1)
```

